---
title: "Binding fMRI - Analyses of feature encoding and integration"
output:
  html_notebook:
    code_folding: hide
    fontsize: 6pt
    theme: cerulean
    toc: yes
    toc_float: yes
  html_document:
    df_print: paged
    toc: yes
---
<style type="text/css">
body{ /* Normal  */
      font-size: 14px}
td {  /* Table  */
  font-size: 12px}
h1.title {
  font-size: 30px}
h1 { /* Header 1 */
  font-size: 24px}
h2 { /* Header 2 */
    font-size: 20px}
h3 { /* Header 3 */
    font-size: 18px}
code.r{ /* Code block */
    font-size: 12px}
</style>


The analyses presented here test subsequent memory effects during encoding of a multi-feature event.  

Mean single trial beta estimates were extracted from each of 204 ROIs across the cortex and medial temporal lobe (see ~/data/bindingfmri_wholebrain_ROIs_info.csv).  

Each event includes 3 associations encoded in parallel -- an object with a i) color, ii) sound, and iii) scene location.  

Subsequent memory is calculated as the number of features (0-3) later correctly recalled, as well as feature-specific estimates of memory (correct, 1, vs. incorrect, 0).  

The relationship between activity (each ROI's beta series) and subsequent memory is estimated using linear mixed effects models with the following pipeline:  

1) Data cleaned by removing outlying betas (z > |4|) within subject and ROI.  
2) Fixed effect predictors are mean-centered (where appropriate).  
3) Model initially specified with a maximal random effects structure, but to avoid convergence problems and singular fits:  
a) Random effects correlations are constrained to zero for all models.  
b) The random effect structure of models with > 2 fixed effect predictors is simplified by iteratively removing slopes that do not change the model fit.  
4) Significance of the fixed effects (slope != 0?) is tested using t-tests with Satterthwaite’s approximation method.

```{r, include=FALSE}

library(ggplot2)
library(ggpubr)
library(ggforce)
library(tidyr)
library(dplyr)
library(knitr)
library(pander)
library(lme4)
library(lmerTest)
library(MuMIn)
library(ez)
library(lsr)
library(psych)
library(reshape2)
library(scales)
library(pracma)
library(mosaic)
library(lessR)


### define computer path
myDir <- '/Users/memolab/Google Drive/MemoLab/Manuscripts/Orbit-Encoding/paper-bindingfmri-repo/'
#myDir <- '/Users/rosecooper/Documents/MemoLab/Manuscripts/Orbit-Encoding/paper-bindingfmri-repo/'

```

# Behavioral Data
```{r}

### Load in behavioral data for all 27 subjects:
behavData <- read.csv(paste(myDir,'data/AllSubjects_bindingfMRI-behavior.csv',sep = ""), header = TRUE)
behav_subs <- unique(behavData$SubID)

# ** note. behavioral data is already sorted by subject and encoding trial onset ** #


# Create additional columns for subsequent memory measures of interest -- Sound, Color, & Scene features ----------------------------
behavData$Sound <- 0
behavData$Sound[behavData$SoundCorrect == 1 & behavData$SoundConfidence == 1] <- 1 # only sucessful if correct *and* high confidence

# define 'success' thresholds for color and scene trials -> 75% probability within von Mises for 27 subject aggregate data
cCutOff = 42
sCutOff = 24

# feature accuracy
behavData$Color <- 0
behavData$Color[behavData$ColAbsError <=cCutOff] <- 1 #correct if error (how far from target) less than or equal to threshold
behavData$Scene <- 0
behavData$Scene[behavData$SceAbsError <=sCutOff] <- 1 #correct if error (how far from target) less than or equal to threshold


# overall memory detail (accounting for feature success - 0-3)
behavData$MemoryDetail <- behavData$Sound + behavData$Color + behavData$Scene


#### separate trial-unique conditions based on feature combinations recalled --------------------
## 1 feature
behavData$Color.Only   <- 0
behavData$Sound.Only <- 0
behavData$Scene.Only   <- 0
behavData$Color.Only[behavData$Color == 1 & behavData$Sound == 0 & behavData$Scene == 0]  <- 1
behavData$Sound.Only[behavData$Color == 0 & behavData$Sound == 1 & behavData$Scene == 0]  <- 1
behavData$Scene.Only[behavData$Color == 0 & behavData$Sound == 0 & behavData$Scene == 1]  <- 1

## 2 features
behavData$Color.Scene   <- 0
behavData$Sound.Color <- 0
behavData$Scene.Sound <- 0
behavData$Color.Scene[behavData$Color == 1 & behavData$Sound == 0 & behavData$Scene == 1] <- 1
behavData$Sound.Color[behavData$Color == 1 & behavData$Sound == 1 & behavData$Scene == 0] <- 1
behavData$Scene.Sound[behavData$Color == 0 & behavData$Sound == 1 & behavData$Scene == 1] <- 1

## 3 features
behavData$Color.Scene.Sound  <- 0
behavData$Color.Scene.Sound[behavData$Color == 1 & behavData$Sound == 1 & behavData$Scene == 1] <- 1


# double check encoding data is sorted correctly (by subject, then encoding onset)
behavData <- behavData[order(behavData$TotalEncodingTrial),]

nTotal <- nrow(behavData)


# print percentage correct for each feature
feature.accuracy <- behavData[,c("TotalEncodingTrial","Color","Sound","Scene")]
kable(feature.accuracy %>% gather(Feature,Accuracy,Color:Scene) %>%
                          group_by(Feature) %>%
                          summarise(Memory = round(mean(Accuracy),3)),format="pandoc",
                                    caption="Feature Accuracy")

### print number of trials that uniquely fall into each possible combination:
cat('\nNone recalled trials =', nrow(subset(behavData,MemoryDetail == 0)),'(',round(((nrow(subset(behavData,MemoryDetail == 0)))/nTotal)*100,2),'%)\n')
cat('Color only trials =', sum(behavData$Color.Only),'(',round(((sum(behavData$Color.Only))/nTotal)*100,2),'%)\n')
cat('Scene only trials =', sum(behavData$Scene.Only),'(',round(((sum(behavData$Scene.Only))/nTotal)*100,2),'%)\n')
cat('Sound only trials =', sum(behavData$Sound.Only),'(',round(((sum(behavData$Sound.Only))/nTotal)*100,2),'%)\n')
cat('Color & Scene only trials =', sum(behavData$Color.Scene),'(',round(((sum(behavData$Color.Scene))/nTotal)*100,2),'%)\n')
cat('Scene & Sound only trials =', sum(behavData$Scene.Sound),'(',round(((sum(behavData$Scene.Sound))/nTotal)*100,2),'%)\n')
cat('Sound & Color only trials =', sum(behavData$Sound.Color),'(',round(((sum(behavData$Sound.Color))/nTotal)*100,2),'%)\n')
cat('Color & Scene & Sound trials =', sum(behavData$Color.Scene.Sound),'(',round(((sum(behavData$Color.Scene.Sound))/nTotal)*100,2),'%)\n')

```

## Check for trial dependencies
Test for the possibility that encoding success at trial t predicts encoding success on trial t+1 (due to proximity of offset betas to onset of next trial). 
```{r}

behavData.shift <- behavData[1:(nrow(behavData)-1),]
behavData.shift$MQNext <- behavData$MemoryDetail[2:nrow(behavData)]

# within subject and run, is there a relationship between memory detail on this trial and memory detail on the next trial?  
behav.model <- lmer(MQNext ~ MemoryDetail + (1+MemoryDetail||SubID/Run), data=behavData.shift)

kable(summary(behav.model)$coefficients, format="pandoc", caption='Dependency between subsequent memory detail on next trial\nand subsequent memory detail on the current trial')
if ((summary(behav.model)$coefficients[2,"Pr(>|t|)"]) > .05) {
  cat('\np > .05 -- No effect of encoding success on trial t on encoding success on trial t + 1')
} else {
   cat('\np < .05 -- Dependency in encoding: encoding success on trial t predicts encoding success on trial t+1')
}

```

# Get ONSET data
```{r}

outlier_value = 4 #SD for removing extreme data (betas)
cat('Removing influential onset betas, |z| >', outlier_value,'\n')

############################# single trial activity data ##############################
# get subjects
subjects <- list.files(path=paste(myDir,'/data/single-trial-betas',sep=""),full.names=TRUE, recursive = TRUE, pattern = 'onset.csv')

allData  = do.call(rbind, lapply(subjects, function(x) {read.csv(x, header = TRUE)}))

allData$SubID=as.factor(allData$SubID)
allData$Trial=as.factor(allData$Trial)
allData$ROI <- as.factor(allData$ROI)
allData <- allData[,-c(4)] # remove vox numbers - not needed here

rois = levels(allData$ROI)



# ******************************************************** #

### add z score of betas within region and subject to remove outliers:
allData <- allData %>%
               group_by(SubID, ROI) %>%
               mutate(Z = zscore(MeanBeta))

# remove betas that are > XSD -- print this number
allData.clean <- allData
allData.clean$MeanBeta[abs(allData.clean$Z) > outlier_value] <- NA  #mark beta as NA if outlier
allData.clean <- allData.clean[,-c(5)] # remove Z values  


##########################################################
#spread data so each of the 204 ROIs is in its own column
myBetas = data.frame(spread(allData.clean, ROI, MeanBeta))
#check still sorted by subject and onset, then add TotalEncodingTrial to match behavioral data:
myBetas <- myBetas[order(myBetas$Trial),]
myBetas <- myBetas[order(myBetas$SubID),]
myBetas$TotalEncodingTrial <- 1:nTotal


# remove all trials where there is at least one NA (at least one of the ROIs is an outlier on that trial):
idxBetas <- complete.cases(myBetas)
cat('Total number of onset outliers removed =',sum(!idxBetas),'out of',nTotal,'\n\n')
myBetas.clean <- myBetas[idxBetas,]


##### merge cleaned betas with behavioral data, removing corresponding behavioral trials:
behavData.clean <- behavData[idxBetas,]
testData <- merge.data.frame(myBetas.clean,behavData.clean,by="TotalEncodingTrial")

# remove duplicate columns for subject and study trial
testData <- testData[,-c(2,3)]
colnames(testData)[colnames(testData) == 'SubID.y'] <- 'SubID'
subjects <- unique(testData$SubID)

onset.data  <- testData  #store as onset betas
onset.behav <- behavData.clean  #store as matching onset behavioral data

cat('Cleaned and merged onset betas and behavioral trials\n')

```

# Get OFFSET data
```{r}

outlier_value = 4 #SD for removing extreme data (betas)
cat('Removing influential offset betas, |z| >', outlier_value,'\n')

############################# single trial activity data ##############################
# get subjects
subjects <- list.files(path=paste(myDir,'/data/single-trial-betas',sep=""),full.names=TRUE, recursive = TRUE, pattern = 'offset.csv')

allData  = do.call(rbind, lapply(subjects, function(x) {read.csv(x, header = TRUE)}))

allData$SubID=as.factor(allData$SubID)
allData$Trial=as.factor(allData$Trial)
allData$ROI <- as.factor(allData$ROI)
allData <- allData[,-c(4)] # remove vox numbers - not needed here

rois = levels(allData$ROI)



# ******************************************************** #

### add z score of betas within region and subject to remove outliers:
allData <- allData %>%
               group_by(SubID, ROI) %>%
               mutate(Z = zscore(MeanBeta))

# remove betas that are > XSD -- print this number
allData.clean <- allData
allData.clean$MeanBeta[abs(allData.clean$Z) > outlier_value] <- NA  #mark beta as NA if outlier
allData.clean <- allData.clean[,-c(5)] # remove Z values  


##########################################################
#spread data so each of the 204 ROIs is in its own column
myBetas = data.frame(spread(allData.clean, ROI, MeanBeta))
#check still sorted by subject and onset, then add TotalEncodingTrial to match behavioral data:
myBetas <- myBetas[order(myBetas$Trial),]
myBetas <- myBetas[order(myBetas$SubID),]
myBetas$TotalEncodingTrial <- 1:nTotal


# remove all trials where there is at least one NA (at least one of the ROIs is an outlier on that trial):
idxBetas <- complete.cases(myBetas)
cat('Total number of offset outliers removed =',sum(!idxBetas),'out of',nTotal,'\n\n')
myBetas.clean <- myBetas[idxBetas,]


##### merge cleaned betas with behavioral data, removing corresponding behavioral trials:
behavData.clean <- behavData[idxBetas,]
testData <- merge.data.frame(myBetas.clean,behavData.clean,by="TotalEncodingTrial")

# remove duplicate columns for subject and study trial
testData <- testData[,-c(2,3)]
colnames(testData)[colnames(testData) == 'SubID.y'] <- 'SubID'
subjects <- unique(testData$SubID)

offset.data  <- testData  #store as onset betas
offset.behav <- behavData.clean  #store as matching onset behavioral data

cat('Cleaned and merged offset betas and behavioral trials\n')

```

# Whole brain analyses
## Memory detail over time
Where across the brain does activity at onset and/or offset linearly scale with memory quantity (0,1,2,3)?  
```{r}

### set up data frame for mixed effect model results:
mixed.data <- data.frame(array(0,c(length(rois)*2,8)))
colnames(mixed.data) <- c('ROI','Phase','Feature','Beta','SE','T','Df','Pvalue')
row = 0


### loop over onset and offset
for (phase in 1:2) {
  
  # gather data so behavioral variables are replicated over each ROI (now as a single column factor)
  if (phase == 1) {
    model.data <- gather(onset.data, ROI, Beta, rois)
    time = 'Onset'
  } else if (phase == 2) {
    model.data <- gather(offset.data, ROI, Beta, rois)
    time = 'Offset'
  }
  
  # ******** run linear mixed effects within each ROI and store data ********** #
  for (r in 1:length(rois)) {
    
    roiData <- subset(model.data, ROI == rois[r])
    roiData$MemoryDetail <- scale(roiData$MemoryDetail, scale = FALSE) # mean-center predictor
    
    # run lmer and get fixed effect stats
    full.model <- suppressMessages(lmer(Beta ~ MemoryDetail + 
                                          (1 + MemoryDetail||SubID), data = roiData))
    stats <- summary(full.model)$coefficients
    nIV <- nrow(stats) # number of fixed effect predictors
    
    ### add fixed effects and p values to data matrix
    mixed.data$ROI[(row+1):(row+nIV-1)]      <- as.character(rois[r])
    mixed.data$Phase[(row+1):(row+nIV-1)]    <- time
    mixed.data$Feature[(row+1):(row+nIV-1)]  <- 'MemoryDetail'
    mixed.data[(row+1):(row+nIV-1),c("Beta","SE","T","Df","Pvalue")] <- stats[2:(nIV),c("Estimate","Std. Error","t value","df","Pr(>|t|)")]
    row = row + nIV -1 #remove intercept
  }
}

#### FDR-correct p-values for multiple comparisons
mixed.data$Pfdr <- 1
p.values <- mixed.data$Pvalue
mixed.data$Pfdr <- p.adjust(p.values, method = "fdr")

## save out parameter estimates and p values as csv file for creating a .nii map of results
write.csv(mixed.data, file = paste(myDir,'analysis/wholebrain-csv-results/memorydetail_effects.csv',sep=""), row.names = FALSE)

cat('Results saved in ~/analysis/wholebrain-csv-results/memorydetail_effects.csv')

```

## Unique feature encoding
After accounting for covariance with the other two features in the model, which areas are uniquely predictd by successful color, scene, or sound encoding?  
```{r}

### set up data frame for mixed effect model results:
mixed.data <- data.frame(array(0,c(length(rois)*6,8)))  # 3 features x 2 times
colnames(mixed.data) <- c('ROI','Phase','Feature','Beta','SE','T','Df','Pvalue')
row = 0

### loop over onset and offset
for (phase in 1:2) {
  
  # gather data so behavioral variables are replicated over each ROI (now as a single column factor)
  if (phase == 1) {
    model.data <- gather(onset.data, ROI, Beta, rois)
    time = 'Onset'
  } else if (phase == 2) {
    model.data <- gather(offset.data, ROI, Beta, rois)
    time = 'Offset'
  }
  
  # ******** run linear mixed effects within each ROI and store data for each feature fixed effect ********** #
  for (r in 1:length(rois)) {
    
    roiData <- subset(model.data, ROI == rois[r])
    roiData$Sound  <- scale(roiData$Sound, scale = FALSE) # mean-center
    roiData$Color  <- scale(roiData$Color, scale = FALSE) # mean-center
    roiData$Scene  <- scale(roiData$Scene, scale = FALSE) # mean-center
    
    # run lmer, simplify random effect structure as > 2 fixed effects, and get fixed effect stats
    full.model <- suppressMessages(suppressWarnings(lmer(Beta ~ Sound + Color + Scene + 
                                                           (1 + Sound + Color + Scene||SubID), data = roiData)))
    full.model <- suppressMessages(suppressWarnings(get_model(step(full.model, reduce.random = TRUE, reduce.fixed = FALSE))))
    stats <- summary(full.model)$coefficients
    nIV <- nrow(stats)
    
    ### add fixed effects and p values to data matrix
    mixed.data$ROI[(row+1):(row+nIV-1)]      <- as.character(rois[r])
    mixed.data$Phase[(row+1):(row+nIV-1)]    <- time
    mixed.data$Feature[(row+1):(row+nIV-1)]  <- row.names(stats)[2:(nIV)]
    mixed.data[(row+1):(row+nIV-1),c("Beta","SE","T","Df","Pvalue")] <- stats[2:(nIV),c("Estimate","Std. Error","t value","df","Pr(>|t|)")]
    row = row + nIV -1 #remove intercept
  }
}

#### FDR-correct p-values for multiple comparisons
mixed.data$Pfdr <- 1
p.values <- mixed.data$Pvalue
mixed.data$Pfdr <- p.adjust(p.values, method = "fdr")

## save out parameter estimates and p values as csv file for creating a .nii map of results
write.csv(mixed.data, file = paste(myDir,'analysis/wholebrain-csv-results/feature_effects.csv',sep=""), row.names = FALSE)

cat('Results saved in ~/analysis/wholebrain-csv-results/feature_effects.csv')

```

# ROI visualization
## Define regions and get data
```{r}

############ get rois ##############
# 1. Offset memory detail response
HIPP    <- c('LH_HIPP')

# 3. Onset memory detail response
IFG   <- c('LH_ContA_PFCl_3','LH_DefaultB_PFCv_4')

# 2. Feature onset effects
VTC   <- c('RH_Limbic_TempPole_4','RH_DorsAttnA_TempOcc_1','RH_VisCent_ExStr_2')  # Color
AUD   <- c('RH_SomMotB_S2_1','LH_SomMotB_Aud_2','LH_SomMotB_Aud_1','RH_SomMotB_S2_2')  # Sound
MTL   <- c('RH_DefaultC_PHC_1','LH_DefaultC_PHC_1','RH_DefaultC_Rsp_1','LH_DefaultC_Rsp_1')  # Scene

myRois <- c(HIPP,IFG,VTC,AUD,MTL)
newRois <- c('HIPP','IFG','VTC','AUD','MTL')
mycolors <- c("#7c67a2","#ff9000","#F64F59","#1D976C","#009FFF")

cat('Regions analyzed:\n\n',
    'HIPP:',HIPP,'\n',
    'IFG:',IFG,'\n',
    'VTC:',VTC,'\n',
    'AUD:',AUD,'\n',
    'MTL:',MTL,'\n')


##### onset data for rois
model.data <- gather(onset.data, ROI, Beta, myRois)
nleft <- length(rois) - length(myRois)
model.data <- model.data[,-c(1:nleft)]

### allocate global ROI
model.data$NewROI[model.data$ROI %in% HIPP] <- 'HIPP'
model.data$NewROI[model.data$ROI %in% IFG] <- 'IFG'
model.data$NewROI[model.data$ROI %in% VTC] <- 'VTC'
model.data$NewROI[model.data$ROI %in% AUD] <- 'AUD'
model.data$NewROI[model.data$ROI %in% MTL] <- 'MTL'

### now summarise within these new ROIs
grouped.data <- model.data %>% group_by(SubID,StudyTrial,NewROI) %>%
                        summarise(NewBeta = mean(Beta))
grouped.data <- spread(grouped.data, NewROI, NewBeta)

myROIData <- merge(grouped.data,onset.behav)
model.data <- gather(myROIData, ROI, Beta, AUD:VTC)
model.data.onset <- model.data


##### offset data for rois
model.data <- gather(offset.data, ROI, Beta, myRois)
nleft <- length(rois) - length(myRois)
model.data <- model.data[,-c(1:nleft)]

### allocate global ROI
model.data$NewROI[model.data$ROI %in% HIPP] <- 'HIPP'
model.data$NewROI[model.data$ROI %in% IFG] <- 'IFG'
model.data$NewROI[model.data$ROI %in% VTC] <- 'VTC'
model.data$NewROI[model.data$ROI %in% AUD] <- 'AUD'
model.data$NewROI[model.data$ROI %in% MTL] <- 'MTL'

### now summarise within these new ROIs
grouped.data <- model.data %>% group_by(SubID,StudyTrial,NewROI) %>%
                        summarise(NewBeta = mean(Beta))
grouped.data <- spread(grouped.data, NewROI, NewBeta)

myROIData <- merge(grouped.data,offset.behav)
model.data <- gather(myROIData, ROI, Beta, AUD:VTC)
model.data.offset <- model.data


###### combined onset and offset data
idx.share <- intersect(model.data.onset$TotalEncodingTrial,model.data.offset$TotalEncodingTrial)
model.onset.clean <- model.data.onset[model.data.onset$TotalEncodingTrial %in% idx.share,]
model.onset.clean$Phase <- 'Onset'
model.offset.clean <- model.data.offset[model.data.offset$TotalEncodingTrial %in% idx.share,]
model.offset.clean$Phase <- 'Offset'

model.data <- rbind(model.onset.clean,model.offset.clean)

cat('\n\nNumber of trials excluded when joining onset and offset betas =',nrow(behavData)-length(idx.share),'/',nrow(behavData))

```

## Subsequent memory
Now predicting memory detail or feature memory with onset and offset beta regressors to get unique variance and run offset - onset contrast per ROI  
```{r, fig.width = 6.5, fig.height = 3}

####################################
mixed.data <- data.frame(array(0,c(length(newRois)*2,7)))
colnames(mixed.data) <- c('ROI','Feature','Beta','SE','T','Df','Pvalue')
row = 0

for (r in 1:length(newRois)) {
  
  roiData <- subset(model.data, ROI == newRois[r])
  roiData <- spread(roiData, Phase, Beta)
  roiData$Onset  <- zscore(roiData$Onset) # standardized
  roiData$Offset <- zscore(roiData$Offset)
  
  if (r <= 2) {  # HIPP or IFG --> memory detail
       roiData$MemoryDetail <- scale(roiData$MemoryDetail, scale = FALSE) # mean-center
       # run lmer, simplify random effect structure, and get fixed effect stats
       full.model <- suppressMessages(lmer(MemoryDetail ~ Onset + Offset + 
                                                     (1 + Onset + Offset||SubID), data = roiData))
  } else if (r == 3) {  # VTC --> Color
       roiData$Color <- scale(roiData$Color, scale = FALSE) # mean-center
       # run lmer, simplify random effect structure, and get fixed effect stats
       full.model <- suppressMessages(lmer(Color ~ Onset + Offset + 
                                              (1 + Onset + Offset||SubID), data = roiData))
  } else if (r == 4) {  # AUD --> Sound
       roiData$Sound <- scale(roiData$Sound, scale = FALSE) # mean-center
       # run lmer, simplify random effect structure, and get fixed effect stats
       full.model <- suppressMessages(lmer(Sound ~ Onset + Offset + 
                                              (1 + Onset + Offset||SubID), data = roiData))
  } else if (r == 5) {  # MTL --> Scene
       roiData$Scene <- scale(roiData$Scene, scale = FALSE) # mean-center
       # run lmer, simplify random effect structure, and get fixed effect stats
       full.model <- suppressMessages(lmer(Scene ~ Onset + Offset + 
                                              (1 + Onset + Offset||SubID), data = roiData))
  }
  
  stats <- summary(full.model)$coefficients
  nIV <- nrow(stats)
  
  # offset - onset (first regressor is intercept)
  print(kable(contest(full.model,c(0,-1,1)), format="pandoc", caption=paste(newRois[r],': Offset - Onset',sep="")))

  ### add fixed effects and p values to data matrix
  mixed.data$ROI[(row+1):(row+nIV-1)]      <- as.character(newRois[r])
  mixed.data$Feature[(row+1):(row+nIV-1)]  <- row.names(stats)[2:(nIV)]
  mixed.data[(row+1):(row+nIV-1),c("Beta","SE","T","Df","Pvalue")] <- stats[2:(nIV),c("Estimate","Std. Error","t value","df","Pr(>|t|)")]
  row = row + nIV -1 #remove intercept
}

mixed.data$ROI <- factor(mixed.data$ROI, levels=newRois)
mixed.data$Feature <- factor(mixed.data$Feature, levels=c('Onset','Offset'))

### print full output:
print(kable(mixed.data,format="pandoc",caption = 'Memory onset and offset fixed effects for ROIs'))


###### plot
ggplot(mixed.data, aes(x=Feature, y=Beta, fill=Feature)) +
     facet_grid(. ~ ROI) +
     geom_hline(yintercept=0,size=1) +
     geom_bar(stat = "identity", alpha = 0.75, size = 1, width = 0.75,
              color = "black", position = position_dodge(1)) +
     scale_fill_manual(values = c("#A6A6A6","#595959")) +
     geom_errorbar(aes(ymin = Beta - SE, ymax = Beta + SE), width = 0.4, size = 1,
                   color = "black", position = position_dodge(1)) +
     theme(plot.title = element_text(hjust = 0.5, size=28, margin=margin(0,0,20,0)),
          axis.line.x = element_line(color = "black", size = 1), axis.line.y = element_line(color = "black", size = 1),
          axis.text.x = element_text(size = 22),
          axis.text.y = element_text(size = 22), axis.title.y = element_text(size = 26),
          axis.title.x = element_blank(), panel.background = element_blank(),
          legend.position="none", strip.text.x = element_text(size=28), text = element_text(family="Helvetica"),
          plot.margin = margin(1, 1, 1, 1, "cm"))

```

## Feature combinations for HIPP
Which specific feature combinations is hippocampus sensitive to?  
```{r, fig.width = 5, fig.height = 4}

####################################
mixed.data <- data.frame(array(0,c(7*2,6)))
colnames(mixed.data) <- c('Feature','Beta','SE','T','Df','Pvalue')
row=0

### loop over onset and offset
for (phase in 1:2) {
  
  # gather data so behavioral variables are replicated over each ROI (now as a single column factor)
  if (phase == 1) {
       roiData <- subset(model.data.onset, ROI == 'HIPP')
       feature = 'Onset'
  } else if (phase == 2) {
       roiData <- subset(model.data.offset, ROI == 'HIPP')
       feature = 'Offset'
  }

  # NOTE. not mean-centering here as zero is meaningful -- excluding trials in other conditions. Implicit baseline = none recalled
  full.model <- suppressMessages(lmer(Beta ~ Color.Only + Sound.Only + Scene.Only +
                                             Color.Scene + Sound.Color + Scene.Sound +
                                             Color.Scene.Sound +
                                             (1 + Color.Only + Sound.Only + Scene.Only +
                                             Color.Scene + Sound.Color + Scene.Sound +
                                             Color.Scene.Sound||SubID), 
                                             data = roiData))
  full.model <- suppressMessages(get_model(step(full.model, reduce.random = TRUE, reduce.fixed = FALSE)))
  stats <- summary(full.model)$coefficients
  nIV <- nrow(stats)

  # test if scene binding is > recalling scene alone (first position is intercept)
  print(kable(contest(full.model,c(0,0,0,-1,(1/3),0,(1/3),(1/3))), format="pandoc", 
              caption=paste('HIPP: Scene Binding vs. Scene Only at ',feature,sep="")))
  
  ### add fixed effects and p values to data matrix
  mixed.data$Phase[(row+1):(row+nIV-1)]    <- feature
  mixed.data$Feature[(row+1):(row+nIV-1)]  <- row.names(stats)[2:(nIV)]
  mixed.data[(row+1):(row+nIV-1),c("Beta","SE","T","Df","Pvalue")] <- stats[2:(nIV),c("Estimate","Std. Error","t value","df","Pr(>|t|)")]
  row = row + nIV -1 #remove intercept
}

### print full output:
print(kable(mixed.data,format="pandoc",caption = 'Feature combinations (vs. none recalled) for L HIPP'))

##### PLOT
order <- c("Color.Only","Scene.Only","Sound.Only","Sound.Color","Color.Scene","Scene.Sound","Color.Scene.Sound")
# colors for venn diagram space feature combinations
barcolors <- c("#f76c67","#67aaf7","#0bca81","#f6a84f","#9c67f7","#67f7f0","#7F7F7F")
mixed.data$Feature <- factor(mixed.data$Feature, levels=order)
mixed.data$Phase <- factor(mixed.data$Phase, levels=c('Onset','Offset'))

ggplot(mixed.data, aes(x=Feature, y=Beta, fill=Feature)) +
     facet_grid(. ~ Phase) +
     geom_hline(yintercept=0,size=1) +
     geom_bar(stat = "identity", alpha = 0.80, size = 1, width = 0.75,
              color = "black", position = position_dodge(1)) +
     scale_fill_manual(values = barcolors) +
     geom_errorbar(aes(ymin = Beta - SE, ymax = Beta + SE), width = 0.4, size = 1,
                   color = "black", position = position_dodge(1)) +
     ggtitle('HIPP encoding activity vs. none recalled') +
     theme(plot.title = element_text(hjust = 0.5, size=28, margin=margin(0,0,20,0)),
          axis.line.x = element_line(color = "black", size = 1), axis.line.y = element_line(color = "black", size = 1),
          axis.text.x = element_text(size = 16, angle = 45,hjust=1,vjust=1),
          axis.text.y = element_text(size = 20), axis.title.y = element_text(size = 24),
          axis.title.x = element_blank(), panel.background = element_blank(),
          legend.position="none", strip.text.x = element_text(size=28), text = element_text(family="Helvetica"),
          plot.margin = margin(1, 1, 1, 1, "cm"))

```
